### 2016-03-22 tips_and_notes/vim/intro.tex
started vim tips intro

@@

So, I started looking at how vim worked and what could be done with it.
What are the advantages?
How are they useful?
What can you do with it?
At first, I was weirded out by the way vim worked, like the modal interface, but I soon became used to it and agreed with the idea of not leaving the home row.
I also discovered multiple plugins that gave the features of the emacs that I loved in the days of undergrad comp sci courses.
The emacs features were based on the configuration file on their computer that I could not reproduce myself, hence I was getting frustrated with the raw emacs that I have installed.

As I read more and more about vim, the urge to learn vim properly became larger.
I had plenty of other options to learn (for example, another programming language), but I chose vim to be my first target - if I could master how to edit text faster, then whatever that follows will also (probably) become faster.
So, I decided to learn vim using the vim tips book ``Practical Vim'' written by Drew Neil.
This part will mostly contain the tips that I thought was very useful from Drew Neil's book, so if you want more details, go and read his book.

>>>>

\section{Why I started using Vim}

@@

So, I started looking at how vim worked and what could be done with it.
What are the advantages?
How are they useful?
What can you do with it?
At first, I was weirded out by the way vim worked, like the modal interface, but I soon became used to it and agreed with the idea of not leaving the home row.
I also discovered multiple plugins that gave the features of the emacs that I loved in the days of undergrad comp sci courses.
The emacs features were based on the configuration file on the comp sci computer (which I could not reproduce myself), hence I was getting frustrated with the raw emacs that I have installed.

As I read more and more about vim, the urge to learn vim properly became larger.
I had plenty of other options to learn before vim (for example, another programming language), but I chose vim to be my first target - if I could master how to edit text faster, then whatever that follows will also (probably) become faster.
So, I decided to learn vim using the vim tips book ``Practical Vim'' written by Drew Neil.
This part of the book will mostly contain the tips that I thought was, or could be, very useful from Drew Neil's book, so if you want more details, go and read his book.

Also, just a note before I start - most sentences will probably be incomplete sentences (bullet-point like), as I am not writing this as a step-by-step guide to vim.
This book is just a bunch of tips I pulled out from his book.
